Zohmg---a large scale data store for aggregated time-series-based data. [DRAFT]

### 2009-05-07 doc/report/msc-report.tex

This thesis fully describes the Zohmg system and how to use it.

@@

In chapter 3 the tools used for the implementation are declared, moving
over to chapter 4 where the details of the implementation are presented.

@@

@@

% ONE DOES NOT SIMPLY PROCESS THE DATA ON ONE COMPUTER INTO MORDOR.
Basically MapReduce is a two phase computation. First the input data is
partitioned and each of these partitions is sent to a \textit{mapper} which
performs computations on each row of the data. The mapper then outputs each
resulting computation on the format \texttt{key,value}. These key-value
pairs are received by a \textit{reducer} which performs the second stage of
the computation.

@@

@@

>>>>

This thesis describes the Zohmg system and how to use it.

@@

In chapter 3, the tools used for the implementation are declared, moving
over to chapter 4 where the details of the implementation are presented.

@@

% TODO> I argue that we should have 'hadoop' and 'hbase' as the main sections,
% and let mapreduce be a subsection of hadooop, bigtable a dito of hbase.

@@

Basically MapReduce is a two phase computation. First the input data is
partitioned and each of these partitions is sent to a \textit{mapper} which
performs computations on each row of the data. The mapper then outputs each
resulting computation on the format \texttt{key,value}. These key-value
pairs are received by a \textit{reducer} which performs the second stage of
the computation.

@@

% TODO> why is this Tool & BigTable-subsection called Dimensions? Disambiguation needed. -fredrik
\subsection{Dimensions}

@@

It'd be interesting to think a bit about how the data store could be fully elastic, i.e. not require any data set definition from the user and instead create column-families on the fly based on the dimensions output from the user's map.
